\thetitle

### 2020-11-21 writing/related.tex
Lots of minor changes and rewordings
edits in related work

\section{Related Work}

This paper builds on~\citet{lksfd-popl-2020}'s one-of-a-kind analysis of
blame for higher-order contracts. They do not spell out the notion of the
rational programmer but the basic ingredients of our technique derive
directly from theirs. Specifically, we adapt their empirical technique
to gradual typing which requires the development of custom mutators,
careful selection of debugging scenarios and generalization of the
technique to allow the comparison of different semantics.

>>>>

\section{Related Work}
\label{sec:related}

This paper builds on~\citet{lksfd-popl-2020}'s human-out-of-the-loop
empirical analysis of
blame for higher-order contracts. They do not spell out the notion of the
rational programmer but the basic ingredients of our technique derive
directly from theirs. Specifically, we revisit their  technique
to bring it to the world of gradual typing which requires the development of custom mutators,
careful selection of debugging scenarios and generalization of the
technique to allow the comparison of different semantics.
